A simplified dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses and coral bleaching as an alternate stable state

### 2017-01-08 JTB_ms/JTB_ms.Rmd
add Fig8 to Makefile

![Bleaching with interactive factors. Simulations of high light stress (sinusoid with maximum=48 mol ph m^-2^ d^-1^) under default environmental conditions (solid line; DIN=1e-7 molN/L; prey=3e-6 CmolX/L), or with elevated feeding (dashed line; prey=6e-6 CmolX/L), or elevated nutrients (dotted line; DIN=1e-6 molN/L). Initial symbiont biomass was set to the steady state for each set of starting conditions, respectively. (All parameters set to default values).](../img/Fig7.png)

@@

![Recovery from bleaching under varying N:C availability. Higher N:C ratios in a heterotrophic food source (effectively representing higher external DIN and/or lower feeding rates) cause a larger overshoot in the S:H biomass ratio, and prolong the duration of time until the system 'recovers' by re-establishing nitrogen-limitation (represented by black dots on each trajectory). All simulations run with default parameters (except varying nNX), and DIN=1e-7 molN/L, prey=1e-6 CmolX/L, and initial symbiont biomass=0.0001.](../img/Fig8.png)

>>>>

![Bleaching with interactive factors. Simulations of high light stress (sinusoid with maximum=48 mol ph m^-2^ d^-1^) under default environmental conditions (solid line; DIN=1e-7 molN L^-1^; prey=3e-6 CmolX L^-1^), or with elevated feeding (dashed line; prey=6e-6 CmolX L^-1^), or elevated nutrients (dotted line; DIN=1e-6 molN L^-1^). Initial symbiont biomass was set to the steady state for each set of starting conditions, respectively. (All parameters set to default values).](../img/Fig7.png)

@@

![Recovery from bleaching under varying N:C availability. Higher N:C ratios in a heterotrophic food source (effectively representing higher external DIN and/or lower feeding rates) cause a larger overshoot in the S:H biomass ratio, and prolong the duration of time until the system 'recovers' by re-establishing nitrogen-limitation (represented by black dots on each trajectory). All simulations run with default parameters (except varying nNX), L=10 mol photons m^2^ d^-1^, DIN=1e-7 molN L^-1^, prey=1e-6 CmolX L^-1^, and initial S:H biomass=0.0001.](../img/Fig8.png)

### 2017-01-08 JTB_ms/JTB_ms.tex
add Fig8 to Makefile

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig7.png}
\caption{Bleaching with interactive factors. Simulations of high light
stress (sinusoid with maximum=48 mol ph m\textsuperscript{-2}
d\textsuperscript{-1}) under default environmental conditions (solid
line; DIN=1e-7 molN/L; prey=3e-6 CmolX/L), or with elevated feeding
(dashed line; prey=6e-6 CmolX/L), or elevated nutrients (dotted line;
DIN=1e-6 molN/L). Initial symbiont biomass was set to the steady state
for each set of starting conditions, respectively. (All parameters set
to default values).}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig8.png}
\caption{Recovery from bleaching under varying N:C availability. Higher
N:C ratios in a heterotrophic food source (effectively representing
higher external DIN and/or lower feeding rates) cause a larger overshoot
in the S:H biomass ratio, and prolong the duration of time until the
system `recovers' by re-establishing nitrogen-limitation (represented by
black dots on each trajectory). All simulations run with default
parameters (except varying nNX), and DIN=1e-7 molN/L, prey=1e-6 CmolX/L,
and initial symbiont biomass=0.0001.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig7.png}
\caption{Bleaching with interactive factors. Simulations of high light
stress (sinusoid with maximum=48 mol ph m\textsuperscript{-2}
d\textsuperscript{-1}) under default environmental conditions (solid
line; DIN=1e-7 molN L\textsuperscript{-1}; prey=3e-6 CmolX
L\textsuperscript{-1}), or with elevated feeding (dashed line; prey=6e-6
CmolX L\textsuperscript{-1}), or elevated nutrients (dotted line;
DIN=1e-6 molN L\textsuperscript{-1}). Initial symbiont biomass was set
to the steady state for each set of starting conditions, respectively.
(All parameters set to default values).}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig8.png}
\caption{Recovery from bleaching under varying N:C availability. Higher
N:C ratios in a heterotrophic food source (effectively representing
higher external DIN and/or lower feeding rates) cause a larger overshoot
in the S:H biomass ratio, and prolong the duration of time until the
system `recovers' by re-establishing nitrogen-limitation (represented by
black dots on each trajectory). All simulations run with default
parameters (except varying nNX), L=10 mol photons m\textsuperscript{2}
d\textsuperscript{-1}, DIN=1e-7 molN L\textsuperscript{-1}, prey=1e-6
CmolX L\textsuperscript{-1}, and initial S:H biomass=0.0001.}
\end{figure}
